A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-16 _01_background.Rmd
rename files'

```{r install_package, eval=FALSE}
# use either devtools or remotes to install
install.packages("devtools")

@@

```{r prep_libs_01_02, eval=FALSE}
# load smoove and datatable
library(smoove)
library(data.table)
library(scales)

>>>>

```{r install_package}
# use either devtools or remotes to install
install.packages("devtools")

@@

```{r prep_libs_01_02}
# load smoove and datatable
library(smoove)
library(data.table)
library(scales)
